---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fika

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/mleary/fika.svg?branch=master)](https://travis-ci.org/mleary/fika)
<!-- badges: end -->

The *fika* package is designed to easily connect people from within a group and (potentially) suggest a topic to kick off the conversation. It's goal is to help connect people.


# What is a Fika?

A fika is Swedish tradition that is similiar to a coffee break.  But a Fika
is much much more than having a coffee. It is a social phenomenon, a 
legitimate reason to set aside a moment for quality time. But don't take if from me, learn
more from the [official Swedish website](https://sweden.se/culture-traditions/fika/).

This approach probably doesn't meet the traditional definition of a fika, but hey the 
goal is to help people interact.

## Installation

You can install fika from Github with the `devtools` package.

``` {r, eval = FALSE}
library(devtools)

devtools::install_github("mleary/fika")
```

## Example

```{r example}
library(fika)

fika::topics[1:3] 

fika::topic_add(fika::topics[1:3], "Favorite restaurant in your town and why?")

dat <- data.frame(
  name = c("Steve", "Kathy", "Tim", "Terry", "Erin", "Emily", "Gail", "Robin", "Denny", "Marge"))

fika::create_groups(dat, min_group_size = 3)

```

