---
title: "Basic Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
 
## Example setup 

```{r setup}
library(fika)

```


## Get participant data

You can source the data anyway you want, via spreadsheet, googlesheets, database,
etc.  The only requirement is you create a dataframe, even if it is only one column.

```{r}
people_in_group <-data.frame(
  people = c("Steve", "Kathy", "Tim", "Terry", "Erin", "Emily", "Gail", "Robin", 
           "Denny", "Marge", "Elizabeth", "Darrell"),
  email = rep("fakeemail@gmail.com", 12)
)

```

## Create topics

Note that the Fika package comes with some suggested topics.  Use the `topics()` 
function to see all the suggested topics.  

```{r}
topics <- fika::topics
topics[1:2]

```

## Add topics
You can add on addtional topics via the `topic_add()` function. Or hey, just 
create your own topics list or ignore it all together.

```{r}
fika::topic_add(topics[1:2], "Favorite restaurant in your town and why?")
```

## Create groups & topics 

Create groups based on the number of people and the min group size you desire.
If you want, you can also create a corresponding topic for each group.

**Please note** that create_groups takes a data frame object.

```{r}
df.groups <- fika::create_groups(people_in_group,
                                min_group_size = 3)

topics <- fika::create_topics(group_nums = 4, topics)
```



